---
title: "Data Developing Products"
author: "Vrinnda"
date: "05/11/2020"
output:
  ioslides_presentation: default
  slidy_presentation: default
---
title: "Books_That_I_love_to_read: An assessment for the my minor certification by esteemeduniversities"
author: "VRINNDA GUPTA"
date: "03/11/2020"
output: ioslides_presentation
----
----
``{r}
library(plotly)
```

## Regarding creating a plot for the Assessment of the course

As for this Assessment, I, Vrinnda Gupta, have taken a database of 'BooksThatILove'. These contain the listings of my favourite books and when they were published.
Now for the same, I have used the RStudios using its language by assessing the datesat presented in the most optimum manner. 
One can thus easily and swiftly navigate throughtout the whole show with use of tab button on the keyboard. 

## Books That I Love

There are a wide range of books that I love in real life, being an avid reader. Thus, this assessment will include a plot which shows the consequent books and their date of publication alongside it. 
All the book names are in the string format, whereas the years are as represened univeresally. 

```{r}
Books_That_I_Love<-c("Les_Miserables","Wonder","Happy_Prince","The_Gift_Of_Maggi","The_Christmas_Carol","Pride_And_Prejudice","War_And_Peace")
Years_Of_The_Books<-c("1862","2012","1888","1905","1843","1813","1867")
plot_the_data<-data.frame(Books_That_I_Love,Years_Of_The_Books)
````

## Plotting for the assessment in the next few steps given 
Now we'll plot the graph for the given data set of books and their specifications. 


```{r}
library(plotly)
plot_ly(data=plot_the_data,x=~Books_That_I_Love,y=~Years_Of_The_Books,type="scatter")%>%
layout(title="Books That I Love and their Years of Publication",xaxis=list(title="Name_Of_The_Books"), yaxis=list(title="Years_Of_Their_Publications"))
````